|

### 2021-09-30 03-Chp-Systematic-Review.Rmd
End of day:
Back to working version

<!-- TODO Discuss Taiwan health database as good evidence on non-Caucasian idenitiies -->

Haag is a good example of potentially missing results - number of cases of other outcoems reported, but no analysis performed.

@@

>>>>

Several eligible studies included in the analysis did not have available results, either due to selective reporting of significant results in conference abstracts,[@su2017; @yamada2009b] or due to the unavailability of supplementary materials containing the relevant results.[@haag2009]

@@

Generalisability was aided by the large number of studies performed using the Taiwan health database, which represents a good sources of evidence on non-Caucasian populations -->
